### 2014-11-10 contract-language.tex
Fixed grammar.

\begin{figure}
\begin{smathpar}
\begin{array}{rclcl}
\multicolumn{5}{c}{
  {x,y,\cureff} \in \mathtt{EffVar} \qquad \qquad
  {\sf Op} \in \mathtt{OperName}
}\\
\cv 		& \in & \mathtt{Contract} 	& \coloneqq & \forall (x : \tau).\cv
        \ALT \pi \\
\tau		& \in	& \mathtt{EffType}	& \coloneqq &  {\sf Op}
        \ALT \tau \vee \tau \\
\pi			&	\in & \mathtt{Prop} & \coloneqq & \true \ALT R(x,y)
        \ALT \pi \vee \pi \\
			  & 		&	 &  \ALT & \pi \wedge \pi \ALT \pi \Rightarrow \pi \\
R				& \in & \mathtt{Relation}	& \coloneqq & \visZ \ALT \soZ
        \ALT \sameobjZ \ALT R^+ \\
				&			&	 &  \ALT & R \cup R \ALT R \cap R \\
\end{array}
\end{smathpar}
\caption{Contract language.}
\label{fig:contract-lang}
\end{figure}

@@

The classification scheme, presented formally in Figure~\ref{sem:classify},
defines rules to judge the consistency class of a contact. For example, the
scheme classifies the \cf{getBalance} contract ($\cv_{gb}$) from
\S~\ref{sec:motivation} as a {\sf\small CausallyConsistent} contract, because
the sequent $\Delta \vdash \ccc \Rightarrow \cv_{gb}$ is valid in first-order
logic (therefore, $\cv_{gb} \le \ccc$), whereas the sequent $\Delta \vdash \ecc
\Rightarrow \cv_{gb}$ is invalid (therefore, $\cv_{gb} \not\le \ecc$). Since we
confine of our contract language to a decidable subset of the logic, validity
of such sequents can be decided mechanically allowing us to automate the
classification scheme in \name.

>>>>

\begin{figure}
\vspace{-7pt}
\begin{smathpar}
\begin{array}{rclcl}
\multicolumn{5}{c}{
  {x,y,\cureff} \in \mathtt{EffVar} \qquad \qquad
  {\sf Op} \in \mathtt{OperName}
}\\
\cv 		& \in & \mathtt{Contract} 	& \coloneqq & \forall (x : \tau).\cv
        \ALT \pi \\
\tau		& \in	& \mathtt{EffType}	& \coloneqq &  {\sf Op}
        \ALT \tau \vee \tau \\
\pi			&	\in & \mathtt{Prop} & \coloneqq & \true \ALT R(x,y)
        \ALT \pi \vee \pi \\
			  & 		&	 &  \ALT & \pi \wedge \pi \ALT \pi \Rightarrow \pi \\
R				& \in & \mathtt{Relation}	& \coloneqq & \visZ \ALT \soZ
        \ALT \sameobjZ \ALT R^+ \\
				&			&	 &  \ALT & R \cup R \ALT R \cap R \\
\end{array}
\end{smathpar}
\caption{Contract language.}
\label{fig:contract-lang}
\end{figure}

@@

The classification scheme, presented formally in Figure~\ref{sem:classify},
defines rules to judge the consistency class of a contact. For example, the
scheme classifies the \cf{getBalance} contract ($\cv_{gb}$) from
\S~\ref{sec:motivation} as a {\sf\small CausallyConsistent} contract, because
the sequent $\Delta \vdash \ccc \Rightarrow \cv_{gb}$ is valid in first-order
logic (therefore, $\cv_{gb} \le \ccc$), whereas the sequent $\Delta \vdash \ecc
\Rightarrow \cv_{gb}$ is invalid (therefore, $\cv_{gb} \not\le \ecc$). Since we
confine our contract language to a decidable subset of the logic, validity
of such sequents can be decided mechanically allowing us to automate the
classification scheme in \name.

### 2014-11-10 intro.tex
Fixed grammar.

The rest of the paper is organized as follows. The next section describes the
system model.  We describe the challenges in programming with eventually
consistent data stores, and introduces \name\ contracts as a proposed solution
to overcome these issues in \S~\ref{sec:motivation}. \S~\ref{sec:lang} provides
more details the contract language, and its mapping to the store consistency
levels, along with meta-theory for certifying the correctness of the mapping.
\S~\ref{sec:txns} introduces transaction contracts and classification.
\S~\ref{sec:impl} describes the implementation and provides details about the
optimizations needed to make the system practical. \S~\ref{sec:results}
discusses experimental evaluation. \S~\ref{sec:related} and~\ref{sec:concl}
present related work and conclusions.

>>>>

The rest of the paper is organized as follows. The next section describes the
system model.  We describe the challenges in programming with eventually
consistent data stores, and introduce \name\ contracts as a proposed solution
to overcome these issues in \S~\ref{sec:motivation}. \S~\ref{sec:lang} provides
more details the contract language, and its mapping to the store consistency
levels, along with meta-theory for certifying the correctness of the mapping.
\S~\ref{sec:txns} introduces transaction contracts and classification.
\S~\ref{sec:impl} describes the implementation and provides details about the
optimizations needed to make the system practical. \S~\ref{sec:results}
discusses experimental evaluation. \S~\ref{sec:related} and~\ref{sec:concl}
present related work and conclusions.
